Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-15 PAPER/main.tex
changed mffd+ pseudocode, using F for feasible solution returned by AHC
changed figure caption, comment about MFFD+ speed, minor change to Comparison

The last heuristic incorporates AHC as described in Section \ref{sec:ahca}. The \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip. However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}). If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip. Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found. Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}). This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution.

\begin{figure}[h!]	
	\centering
	\includestandalone[width=\textwidth]{figures/strips}
	\caption{Comparison of MFFD and MFFD$^+$, $W = 20$, $\tau = 70$.}	
	\label{fig:comparestrips}
\end{figure}

\section{Comparison}
For our experiments, we used sets $\mathcal{I}$ containing 100, 500, and 1000 items. We generated 1000 different problem instances for each size of $\mathcal{I}$. For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution. Three different strip widths $W$ were used, 5000, 2500, and 1250. As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult. Both the items and the strips have equal height of $H = 1$.

\subsection{Problem Instances}
\begin{itemize}
	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$, same 1000 instances for each run
	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
	\item items and strips have equal height $H = 1$, strips have three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
	\item As the strip width decreases, the number of items/strip decreases, making the problem more difficult, changes the average number of items per strip (why is this important?)
	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
	\item Values for $\delta$ from 0.0 to 1.0 in increments of 0.1 are calculated by changing the value of $\tau$. 
	\item Thus, if $\delta  = 0.0$, then there are no score widths that can feasibly be aligned together, and hence $|\mathcal{I}|$ strips are required (one for each item), whereas if $\delta = 1.0$, then all pairs of score widths meet the vicinal sum constraint (i.e. sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP. 
	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
\end{itemize}

>>>>

The last heuristic incorporates AHC as described in Section \ref{sec:ahca}. The \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip. However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}). If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip. Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found. Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}). This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution. Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.

\begin{figure}[h!]	
	\centering
	\includestandalone[width=\textwidth]{figures/strips}
	\caption{Example instance of the sub-problem, with $W = 20$ and $\tau = 70$. In MFFD the constraint is not fulfilled in either orientation, however MFFD$^+$ is able find a feasible arrangement.}	
	\label{fig:comparestrips}
\end{figure}

\section{Comparison}
For our experiments, we generated 1000 problem instances for three different sizes of $\mathcal{I}$, containing 100, 500, and 1000 items. For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution. Three different strip widths $W$ were used, 5000, 2500, and 1250. As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult. Both the items and the strips have equal height of $H = 1$.

\begin{itemize}
	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$, same 1000 instances for each run
	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
	\item items and strips have equal height $H = 1$, strips have three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
	\item As the strip width decreases, the number of items/strip decreases, making the problem more difficult, changes the average number of items per strip (why is this important?)
	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
	\item Values for $\delta$ from 0.0 to 1.0 in increments of 0.1 are calculated by changing the value of $\tau$. 
	\item Thus, if $\delta  = 0.0$, then there are no score widths that can feasibly be aligned together, and hence $|\mathcal{I}|$ strips are required (one for each item), whereas if $\delta = 1.0$, then all pairs of score widths meet the vicinal sum constraint (i.e. sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP. 
	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
\end{itemize}
